---
title: "Fancy Map App"
author: "mbandi"
date: "`r Sys.Date()`"
output: 
    ioslides_presentation: 
      transition: slower
      theme: cosmo
      highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Fancy Map App

Printing information on top of a map is easy. 

But what about detecting when the user clicks something inside the map?

That's easy too!

With the Fancy Map App you can learn how to handle user clicks events in leaflet

> - While also knowing were to go for some nice views
> - Or to see some fancy art
> - Or where to get the best ice cream


## Map functionality

The user can select the types of markers to be shown easily by clicking the categories in the map itself.
It has the information organized in tabs to keep things tidy.

- The 'Info' tab contains a brief user manual, in case it's needed

- The 'Details tab has information about the selected marker

- The 'Distance' tab shows the distance between two markers


## Distance calculation

To calculate the distance between two markers the raster package is used.
It's simple to use, it just needs the coordinates and returns the distance in meters.

```{r load, echo=TRUE, message=FALSE}
library(raster)
```

```{r dist, echo=TRUE}
centralParkSouth <- c(-73.979005, 40.766994)
centralParkNorth <- c(-73.955402, 40.799412)
pointDistance(centralParkSouth, centralParkNorth, lonlat = TRUE)
```

## Links

You can check the live app here:
[https://mbandi.shinyapps.io/FancyMap/](https://mbandi.shinyapps.io/FancyMap/)

The source code is in github:
[https://github.com/mbandi/ProgrammingAssignment13](https://github.com/mbandi/ProgrammingAssignment13)

> - Thank you!