---
title: "Fancy Map App"
author: "mbandi"
date: "`r Sys.Date()`"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Fancy Map App

The Fancy Map App is an extension of the leaflet assignment.


It has a sidebar with two tabs

    - The first tab is used to display the selected marker description.
    - The second tab is used to show the distance between two markers. 

The main panel is for the map

    - Each marker has it's own popup and id, and belongs to a group.
    - Groups can be shown/hidden with the checkboxes from the map.

## Map functionality

Selecting a marker will change the description shown in the 'Description' tab, but also save that marker for the distance calculation.

When clicking multiple markers, the first one is kept, and the second is overridden. 

To select a new initial marker there is a reset button in the 'Distance' tab.

## Interaction and observers

Most of the interaction occurs by selecting markers on the map. For this reason most of the changes are handled inside the `observeEvent(input$map_marker_click, {...})` event:

    - Updates the description text
    - Store the marker as either `markerA` or `markerB` (and the associated text)
    - Updates the distance between the two selected markers
    
The `Reset` button has it's own observer and it's only purpose is to clear the selected markers and set the corresponding message

## Distance calculation

To calculate the distance between two markers I use the raster package.
It's simple to use, it just needs the coordinates and returns the distance in meters.

```{r load, echo=TRUE, message=FALSE}
library(raster)
```

```{r dist, echo=TRUE}
centralParkSouth <- c(-73.979005, 40.766994)
centralParkNorth <- c(-73.955402, 40.799412)
pointDistance(centralParkSouth, centralParkNorth, lonlat = TRUE)
```
